DSSynth: An Automated Synthesis Tool of Digital \\ Controllers for Physical Plants via MATLAB Toolbox

### 2017-06-05 ase2017/paper.tex
improved llustrative Example
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\usepackage{xspace,framed}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{subfig} 
\usepackage{xcolor,colortbl}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{cite}	
\usepackage{mathtools}

@@

\title{DSSynth: An Automated Controller Synthesis Tool \\ for Physical Plants via MATLAB Toolbox}

@@

A graphical user interface application was developed (Fig.~\ref{fig:gui-for-tf}) 
to favor digital controller synthesis in MATLAB, besides improving usability and, 
consequently, attracting more digital dynamical system engineers. Users can provide all 
required parameters for digital controller synthesis: physical plant specification, 
fixed-point representation and dynamic inputs. 
%

\begin{figure}[ht]
    \centering
    \subfloat[Define representation and the physical plant.]{
		\includegraphics[width=0.35\textwidth]{step1.png}
		\label{step1}}
		\hfil
    \subfloat[Determine the implementation and the dynamic range.]{
	\includegraphics[width=0.35\textwidth]{step2.png}
		\label{step2}}
		\hfil
    \subfloat[Digital controler synthesized.]{
	\includegraphics[width=0.35\textwidth]{step3.png}
		\label{step2}}
		\hfil
    \subfloat[Step Response for the stable digital controller synthesized]{
	\includegraphics[width=0.35\textwidth]{step4.png}
		\label{step3}}
		\hfil
    \caption{GUI application for the digital synthesis based on the transfer function representation.}
    \label{fig:gui-for-tf}
\end{figure}

@@

Our experimental evaluation consist of a set of control system benchmarks,
which include physical plants for UAV, cruise control, spring-mass damper,
satellite, direct current (DC) servo motor, helicopter, inverted pendulum,
magnetic suspension, computer tape driver, robot manipulator, flexible beam,
guidance system, and an antenna control system~\cite{abate2017, abatecav2017}.

>>>>

\usepackage{xspace,framed}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{subfigure} 
\usepackage{xcolor,colortbl}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{cite}	
\usepackage{mathtools}

@@

\title{DSSynth: An Automated Synthesis Tool of Digital \\ Controllers for Physical Plants via MATLAB Toolbox}

@@

A graphical user interface application was developed (Fig.~\ref{fig:gui-for-tf}) 
to favor digital controller synthesis in MATLAB, besides improving usability and, 
consequently, attracting more digital dynamical system engineers. Users can provide all 
required parameters for digital controller synthesis: physical plant specification, 
fixed-point representation and dynamic inputs. 
%
\begin{figure}
  \includegraphics[width=0.5\textwidth]{screens_dssynth.png}
  \caption{GUI application for the digital controller synthesis based on the transfer function representation.}
  \label{fig:gui-for-tf}
\end{figure}

@@
